Self Regulation Ontology Retest Data Report

### 2017-04-05 SRO_Report.Rmd
working in report

```{r warning=FALSE, message=FALSE}
ggplot_build(icc_df %>%
               ggplot(aes(eta_sq, fill=task)) +
               geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
  mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
  get_labels(.,icc_df, "eta_sq", "task") %>%
  prettify_label(.) %>%
  filter(bin != 1 & bin !=2 & !is.na(label)) %>%
  select(label)

anyNA("NA") 
```

>>>>

```{r warning=FALSE, message=FALSE, fig.height=72}
time_effect_vars = ggplot_build(icc_df %>%
               ggplot(aes(eta_sq, fill=task)) +
               geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
  mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
  get_labels(.,icc_df, "eta_sq", "task") %>%
  prettify_label(.) %>%
  filter(bin != 1 & bin !=2 & label != "NA") %>%
  select(label, task) %>%
  separate(label,into=c(as.character(1:27)),sep = "</br>") %>%
  gather(key, value, -task) %>%
  select(value, task) %>%
  na.omit()

time_effect_vars$value = gsub("\"", "", time_effect_vars$value)

for(i in 1:nrow(time_effect_vars)){
  tmp = rbind(tmp, match_t1_t2(time_effect_vars$value[i]))
}
rm(time_effect_vars)

tmp %>%
  spread(time, score) %>%
  # mutate(dv_wrap = str_wrap(dv, width = 30)) %>%
  ggplot(aes(`1`, `2`))+
  geom_point()+
  theme_bw()+
  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())+
  geom_abline(intercept = 0, slope=1)

tmp

tmp %>% 
  outer_join(icc_df[,c("dv", "eta_sq"), by="dv"])
